---
title: "Wisconsin Districts"
author: "Liesl Eckstrom"
sidebar: false
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
library(tidyverse)
library(mdsr)     
library(sf)
library(ggspatial)
library(prettymapr)
library(mapproj)
library(maps)
library(fec16)
library(leaflet)
library(ggplot2)
```

```{r, include = FALSE}
#| message: false
#| warning: false

print(results_house, width = Inf)
results_house |>
  group_by(state, district_id) |>
  summarize(N = n())
```


```{r, include = FALSE}
#| message: false
#| warning: false

# summary of the 13 congressional NC districts and the 2012 voting
district_elections <- results_house |>
  mutate(district = parse_number(district_id)) |>
  group_by(state, district) |>
  summarize(
    N = n(), 
    total_votes = sum(general_votes, na.rm = TRUE),
    d_votes = sum(ifelse(party == "DEM", general_votes, 0), na.rm = TRUE),
    r_votes = sum(ifelse(party == "REP", general_votes, 0), na.rm = TRUE),
    .groups = "drop"
  ) |>
  mutate(
    other_votes = total_votes - d_votes - r_votes,
    r_prop = r_votes / total_votes,  
    winner = ifelse(r_votes > d_votes, "Republican", "Democrat")
  )
wi_results <- district_elections |>
  filter(state == "WI")
wi_results |>                  
  select(-state)
```


```{r, include = FALSE}
# distribution of total number of votes is narrow by design
wi_results |>
  skim(total_votes) |>
  select(-na)

# compare total Dem and Rep votes across wi in 2012
wi_results |>
  summarize(
    N = n(), 
    state_votes = sum(total_votes), 
    state_d = sum(d_votes), 
    state_r = sum(r_votes)
  ) |>
  mutate(
    d_prop = state_d / state_votes, 
    r_prop = state_r / state_votes
  )

# Proportion of Rep votes by district
wi_results |>
  select(district, r_prop, winner) |>
  arrange(desc(r_prop))
```

```{r, include = FALSE}
#| message: false
#| warning: false

# Download congressional district shapefiles for the 113th Congress from a UCLA website (don't sweat the details too much)
src <- "http://cdmaps.polisci.ucla.edu/shp/districts113.zip"
lcl_zip <- fs::path(tempdir(), "districts113.zip")
download.file(src, destfile = lcl_zip)
lcl_districts <- fs::path(tempdir(), "districts113")
unzip(lcl_zip, exdir = lcl_districts)
dsn_districts <- fs::path(lcl_districts, "districtShapes")

# You can also downloaded zip file and uploaded it into R, but this uses a ton of space!
# dsn_districts <- fs::path("Data/districtShapes")

# read shapefiles into R as an sf object
st_layers(dsn_districts)

# be able to read as a data frame as well
districts <- st_read(dsn_districts, layer = "districts113") |>
  mutate(DISTRICT = parse_number(as.character(DISTRICT)))
head(districts, width = Inf)
class(districts)

# create basic plot with wi congressional districts
wi_shp <- districts |>
  filter(STATENAME == "Wisconsin")
wi_shp |>
  st_geometry() |>
  plot(col = gray.colors(nrow(wi_shp)))

# Append election results to geospatial data
wi_merged <- wi_shp |>
  st_transform(4326) |>
  inner_join(wi_results, by = c("DISTRICT" = "district"))
head(wi_merged, width = Inf)

# Color based on winning party
#   Note that geom_sf is part of ggplot2 package, while st_geometry is
#   part of sf package
```

```{r, echo = FALSE}
# A leaflet map can allow us to zoom in and see where major cities fit, etc.
pal <- colorNumeric(palette = "RdBu", domain = c(0, 1))

leaflet_wi <- leaflet(wi_merged) |>
  addTiles() |>
  addPolygons(
    weight = 1, fillOpacity = 0.7, 
    color = ~pal(1 - r_prop),   # so red association with Reps
    popup = ~paste("District", DISTRICT, "</br>", round(r_prop, 4))
  ) |>                          # popups show prop Republican
  setView(lng = -90, lat = 45, zoom = 6)
leaflet_wi
```


This map of Wisconsin shows the 7 senate districts from 2016 and they are shaded according to proportion of votes for each party in that district (red = republican, blue = democrat). When you click on each district you also get two articles of information, which district you are looking at, and the proportion of republican votes in that district. This is important information because it tells us how much more or less than 50% each district votes republican and gives us an idea of voting demographics and why the districts may be split like they are. 
