---
title: "Mini Project 2"
author: "Liesl Eckstrom"
sidebar: false
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(tidyr)
library(Stat2Data)
library(ggplot2)
library(ggthemes)
data("Handwriting")
```

```{r}
t.test(Both ~ Gender, data = Handwriting)
```

```{r}

handwriting_small <- Handwriting |> 
  drop_na() |>
  mutate(gender = Gender, perc_correct = Both) |> 
  select(gender, perc_correct) |>
  group_by(gender) |>
  summarize(avg_perc = mean(perc_correct))

gender_diff <- handwriting_small[[2]][2] - handwriting_small[[2]][1]


sim_gender_diffs <- vector("double", 1000)
for(i in 1:1000) {
  handwriting_small <- Handwriting |>
    drop_na() |>
    mutate(gender = Gender, 
           perc_correct = Both, 
           gender = sample(gender)) |>
    group_by(gender) |>
    summarize(avg_perc = mean(perc_correct))
  sim_gender_diffs[[i]] <- handwriting_small[[2]][2] - handwriting_small[[2]][1]
}  

sim_null_world <- tibble(sim_gender_diffs = sim_gender_diffs)
ggplot(sim_null_world, aes(x = sim_gender_diffs)) +
  geom_histogram(aes(y = after_stat(density)), color = "lightgrey", fill = "lightgrey", binwidth = 0.5) +
  geom_density(col = "black") +
  geom_vline(xintercept = gender_diff, color = "hotpink") +
  labs(title = "Simulated Null World",
       subtitle = "with observation marker",
       caption = "data from: Stat2Data package"
       ) +
  theme_void()

find_p <- function(x,y) {
  p_value <- sum(abs(x) >= abs(y)) / 1000
  
p_value
}

find_p(sim_gender_diffs, gender_diff)


```

For this project I used the Handwriting dataset from the Stat2Data R package. The Handwriting dataset comes from a survey where participants were asked to identify the gender of the author based on the handwriting presented. I chose to look at the relationship between gender of the participant and average performance (by gender) on the survey. The x-axis of the graph represents the simulated gender differences in average correct identification of handwriting. I used a loop to simulate the null world by shuffling the data 1000 times and recording the difference of the average between genders after each one.

This graph shows the simulated null world distribution and has a vertical line marker that represents the real world observation. The p-value for this observation is \< **0.001**. When I calculated the p-value for this observation (given my simulation of 1,000 events) I get the number 0 because my observation or something higher didn't happen in the 1,000 simulated trials, but the p-value is never truly exactly zero. The size of this p-value means that women's performance was statistically significantly higher than men's performance on the survey.
