---
title: "Mini Project 2"
author: "Liesl Eckstrom"
sidebar: false
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
library(tidyverse)
library(tidyr)
library(Stat2Data)
library(ggplot2)
library(ggthemes)
data("Handwriting")
```

```{r, include = TRUE}
t.test(Both ~ Gender, data = Handwriting)
```

```{r, echo = TRUE}

handwriting_small <- Handwriting |> 
  drop_na() |>
  mutate(gender = Gender, perc_correct = Both) |> 
  select(gender, perc_correct) |>
  group_by(gender) |>
  summarize(avg_perc = mean(perc_correct))

gender_diff <- handwriting_small[[2]][2] - handwriting_small[[2]][1]


sim_gender_diffs <- vector("double", 1000)
for(i in 1:1000) {
  handwriting_small <- Handwriting |>
    drop_na() |>
    mutate(gender = Gender, 
           perc_correct = Both, 
           gender = sample(gender)) |>
    group_by(gender) |>
    summarize(avg_perc = mean(perc_correct))
  sim_gender_diffs[[i]] <- handwriting_small[[2]][2] - handwriting_small[[2]][1]
}  

sim_null_world <- tibble(sim_gender_diffs = sim_gender_diffs)
ggplot(sim_null_world, aes(x = sim_gender_diffs)) +
  geom_histogram(aes(y = after_stat(density)), color = "lightgrey", fill = "lightgrey", binwidth = 0.5) +
  geom_density(col = "black") +
  geom_vline(xintercept = gender_diff, color = "hotpink") +
  labs(title = "Simulated Null World",
       subtitle = "with observation marker",
       caption = "data from: Stat2Data package",
       ) +
  theme_void()

find_p <- function(x,y) {
  p_value <- sum(abs(x) >= abs(y)) / 1000
  
p_value
}

find_p(sim_gender_diffs, gender_diff)


```



For this project I used the Handwriting dataset from the Stat2Data R package. The Handwriting dataset comes from a survey where participants were asked to identify the gender of the author based on the handwriting presented. I chose to look at the relationship between gender of the participant and average performance (by gender) on the survey. I used a loop to simulate the null world by shuffling the data 1000 times and recording the difference of the average between genders after each one. 

This graph shows the simulated null world distribution and has a vertical line marker that represents the real world observation. The p-value for this observation is **0**. This means that women's performance was statistically significantly higher than men's performance on the survey.

**i know that my p_value is not actually zero, is this just because in the null world it didn't happen in 1,000 tries but it could potentially happen in the null world**

**is it okay that there is no x lab because this theme doesn't support x labs I want consistency across the things on my website and my othe graph has this theme**

